---
title: "Lab2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Exercise 1
```{r, message=FALSE}
library(tidyverse)
```

```{r}
housing <- read_csv("http://colindawson.net/data/landdata-states.csv")
glimpse(housing)
help.search("geom_", package = "ggplot2")
```

###Exercise 2
```{r}
hp2013Q1 <- housing %>% filter(Date == 2013.25)
ggplot(hp2013Q1, aes(Home.Value, x=Land.Value)) + geom_point()
```

```{r}
base_plot <- ggplot(hp2013Q1, aes(y = Structure.Cost, x = Land.Value))
base_plot + geom_point()
```

###Exercise 3
```{r}
home_value_plot <- ggplot(hp2013Q1, aes(y = Structure.Cost, x = Land.Value)) + geom_point()
```

```{r}
home_value_plot + geom_line()
```
###Exercise 4
It may not make sense to connect the points with lines in this case. The lines are connecting points with different land and home values; each line connects a point to the nearest land values on each side, allowing you to see the change in the structure cost for land values of adjacent size. It doesn't seem particularly helpful to see lines from each land value to the next; a regression line for the data may be more useful

```{r}
base_plot +
  geom_point()

base_plot +
  geom_smooth()

base_plot +
  geom_point() + 
  geom_smooth()
```

```{r}
base_plot + 
  geom_text(aes(label = State), size = 3)
```

```{r}
base_plot <- base_plot +
  aes(color = Home.Value)
```

###Exercise 5
```{r}
home_value_plot + aes(color = Structure.Cost) + geom_point()
```

```{r}
base_plot +
  geom_point(aes(shape = region)) + scale_shape_discrete()
```

```{r}
home_plot <- ggplot(housing, aes(y = State, x = Home.Price.Index)) +
  geom_point(aes(color = Date),
             alpha = 0.3,
             size = 1.5,
             position = position_jitter(width = 0, height = 0.25))
home_plot <- home_plot +
  scale_y_discrete(name = "State Abbreviation")
home_plot +
  scale_color_continuous(breaks = c(1975.25, 1994.25, 2013.25),
                         labels = c(1971, 1994, 2013))
home_plot <- home_plot +
  scale_color_continuous(
    breaks = c(1975.25, 1994.25, 2013.25),
    labels = c(1971, 1994, 2013),
    low = "blue", high = "red")
home_plot

home_plot +
  scale_color_gradient2(
    breaks = c(1975.25, 1994.25, 2013.25),
    labels = c(1971, 1994, 2013),
    low = "blue", high = "red", mid = "gray60",
    midpoint = 1994.25)
```

###Exercise 6
```{r}
home_plot +
  scale_color_gradient2(
    breaks = c(1975.25, 1994.25, 2013.25),
    labels = c(1971, 1994, 2013),
    low = "blue", high = "red", mid = "gray60",
    midpoint = 1994.25) +   geom_vline(aes(xintercept = 1), linetype = 4, color = "black")
```

###Exercise 7
You would do so by putting the command to add the line earlier in the sequence, like in the code below:
```{r}
ggplot(housing, aes(y = State, x = Home.Price.Index)) + geom_vline(aes(xintercept = 1), linetype = 4, color = "black") + geom_point(aes(color = Date), alpha = 0.3, size = 1.5, position = position_jitter(width = 0, height = 0.25)) + scale_y_discrete(name = "State Abbreviation") + scale_color_continuous(breaks = c(1975.25, 1994.25, 2013.25), labels = c(1971, 1994, 2013)) + scale_color_gradient2(
    breaks = c(1975.25, 1994.25, 2013.25),
    labels = c(1971, 1994, 2013),
    low = "blue", high = "red", mid = "gray60",
    midpoint = 1994.25)
```

```{r}
state_plot <- ggplot(housing, aes(x = Date, y = Home.Value))

state_plot +
  geom_line(aes(color = State))
```

```{r}
state_plot +
  geom_line() +
  facet_wrap(~State, ncol = 10)
```
###Exercise 8
```{r}
region_plot <- ggplot(housing, aes(x = Year, y = Land.Value))

region_plot + geom_line() + facet_wrap(~region, ncol = 2)

```
